Calculating Entropies With Nested Sampling

### 2017-02-13 paper/ms.tex
Wrote a tiny bit of NS prelude stuff

When $N=1$, the sequence of $X$ values is a Poisson process.

\citet{Walter2015} showed how this view of the NS sequence of points
can be used to construct a
version of NS that produces unbiased estimates of the marginal likelihood.
However, it can also be used to construct an unbiased estimator of
a log-probability, which is more relevant to information theoretic
quantities.

>>>>

When $N=1$, the sequence of $\ln X$ values is a Poisson process with rate
1. \citet{Walter2015} showed how this view of the NS sequence of points
can be used to construct a
version of NS that produces unbiased estimates of the marginal likelihood.
However, it can also be used to construct an unbiased estimator of
a log-probability, which is more relevant to information theoretic
quantities.

Given the definition of the NS algorithm,
the probability distribution for the proportion $t$ of the prior mass
retained on a given iteration is
\begin{align}
t_i &\sim \textnormal{Beta}(N, 1),
\end{align}
and the probability distribution for the sequence of $X$-values is
obtained from
\begin{align}
X_i &= \prod_{k=1}^i t_i.
\end{align}
